Modeling and Simulation of Load Balancing Strategies for Computing in High Energy Physics

### 2018-10-09 paper/paper.tex
Add seff

\section{Modeling Computing Jobs and Resources}
\label{sec:model}\todo{Grafik?}
This section describes how the computing jobs and working nodes are modeled using Palladio.
The component model describes each type of CMS computing job, such as analysis or reprocessing jobs, with their resource demands. These demands are the \textit{CPU demand}, the\textit{ I/O demand}, the \textit{number of used CPU cores}, the \textit{required job slot}s, and the \textit{number of processed events}.

After a job is scheduled on a resource container, it acquires the specified number of job slots or waits if the node has not sufficient free slots. Afterwards, the CPU and I/O demands of the job are processed. To avoid one big I/O operation at the start of a job and to make the processing of I/O more continuously, the processing is modeled using iterations that reflect the number of events. Thus, for each iteration there are I/O and CPU resources needed. Rather than simulating each event, we simulate a fraction of the processed events, because the simulation of each event would harm the scalability of the simulation. 
While processing, the job uses the specified number of cores to process the CPU demand. After the job finished, it releases its acquired job slots. All of these parameters are specified as a probability function and are extracted from measured performance data as described in \Cref{sec:param}.

@@

Simulating one week of CMS jobs at GridKa takes about 18 minutes on a laptop. Thus, it would feasible to simulate several Tiers at once in a sufficient time. However, for simulating larger parts of the WLCG a more macroscopic model, which focuses on the interaction of the Tiers and does not model their inner structure in detail,
is recommended. \todo{Formulierung nicht passiv. Positiver: How to aggregate is future work?}

@@

We successfully simulated the CMS computing jobs at GridKa. To enable easy usage of the simulation we implemented an automated model parameter extraction and model creation. Furthermore, we extended Palladio to be able to simulate load balancing strategies. Our first results suggest that this approach could deliver accurate results regarding CPU efficiency, however it must be investigated what the reason for the data inconsistency and missing job information is. Regarding scalability we are confident that several computing centers could be simulated on a detailed level. For use cases that require the simulation of larger parts of the WLCG we suggest a more macroscopic model that focuses on the interaction of the sites and models the sites internals on a less detailed level.

>>>>

\section{Modeling Computing Jobs and Resources}
\label{sec:model}
This section describes how the computing jobs and working nodes are modeled using Palladio.
The component model describes each type of CMS computing job, such as analysis or reprocessing jobs, with their resource demands. These demands are the \textit{CPU demand}, the\textit{ I/O demand}, the \textit{number of threads}, the \textit{required job slots}, and the \textit{number of demand rounds}.

\Cref{seff} shows the behaviour of the job during the simulation. After a job is scheduled on a resource container, it acquires the specified number of job slots or waits if the node has not sufficient free slots. Afterwards, the CPU and I/O demands of the job are processed. To avoid one big I/O operation at the start of a job and to make the processing of I/O more continuously, the processing is modeled using iterations that reflect the number of processed events. Thus, for each iteration there are I/O and CPU resources needed. Rather than simulating each event, we simulate a fraction of the processed events, because the simulation of each event would harm the scalability of the simulation. 
While processing, the job uses the specified number of threads to process the CPU demand. After the job finished, it releases its acquired job slots. All of these parameters are specified as a probability function and are extracted from measured performance data as described in \Cref{sec:param}.

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{images/seff}
	\caption[]{Model of Job Behaviour}
	\label{seff}
\end{figure}

@@

Simulating one week of CMS jobs at GridKa takes about 24 minutes on a laptop. Thus, it would feasible to simulate several Tiers at once in a sufficient time, however simulating larger parts of the grid is future work.

@@

We successfully simulated the CMS computing jobs at GridKa. To enable easy usage of the simulation we implemented an automated model parameter extraction and model creation. Furthermore, we extended Palladio to be able to simulate load balancing strategies. Our first results are promising and suggest that this approach can be used to simulate load balancing strategies accurately. Regarding scalability we are confident that several computing centers can simulated in a sufficient time, however this is part of future work.
